Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-18 doc/main_jfm.tex
figure 0 caption

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for the mobility problem. 
Particles self-assemble into vesicle bilayers (panel (b)). In panel (c), 
the particles arrange along inner and outer leaflets. The curve $C_M$ is the midplane curve which has 
length $L$ and surrounds a region of area $A$.  Initially stretched vesicles relax to equilibrium 
with fluid flow across the bilayer. The study considers a single vesicle in shear flow (panel (d)) and other background flows
and considers vesicle interactions in background flows (panel (e)).}
\label{fig:figure0}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for the mobility problem. 
The color map in panels (b) - (e) is the solution $u$ of \eqref{eq:SL}. Red indicates a high degree of hydrophobicity ($u = 1$) 
while blue indicates no hydrophobicity ($u = 0$).
Particles self-assemble into vesicle bilayers (panel (b)) and eventually  
arrange along inner and outer leaflets (panel (c)). The curve $C_M$ is the midplane curve which has 
length $L$ and surrounds a region of area $A$.  Initially stretched vesicles relax to equilibrium 
with fluid flow across the bilayer. The study considers a single vesicle in background flows such as shear flow (panel (d))
and hydrodynamic vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}
